The natural history of scavenging in vertebrates

### 2016-03-04 natural history of scavenging.tex
intro update

\section*{Introduction}
%TG: it might be better to reorganise the intro as:
%§1 - scavenging is understudied because it's hard to say who's a scavenger
%§2 - it's even more problematic in the fossil record but people have tried some indirect approaches
%§3 - good thing is that we can apply these indirect approaches to extant systems
%§4 - in this review we discuss some stuff.
%TG: or something along these lines, obviously flexible!

@@

"\cite{sazima1990necrofagia} predict-ed  that  several  components  of  snake  be-havior contribute to scavenging propensity. They  postulated  that  snakes  that  rely  on chemosensory information to acquire prey might  forage  for  carrion  more  frequently than  those  whose  modes  of  prey  acquisi-tion are driven by visual cues. Additionally, \cite{sazima1990necrofagia} suggested that habitat and diet preferences might be indicators   of   scavenging   propensity   be-cause  they  influence  the  likelihood  of  a particular  species  encountering  carrion naturally. Based on these criteria, they pre-dicted that aquatic or semi-aquatic pisciv-orous  snakes  would  scavenge  more  fre-quently than other species. Moreover, \cite{sazima1990necrofagia}   suggested that  water  currents  that  induce  aggrega-tions of carrion heighten the probability of carrion detection by these snakes (see also \cite{savitzky1992laboratory}).  Also,  chemical  gradients may  be  more  uniform  and  give  more  de-pendable  directional information in water \citep{sazima1990necrofagia}." \citep{devault2002scavenging}

>>>>

\section*{Introduction}
%TG: it might be better to reorganise the intro as:
%§1 - scavenging is understudied because it's hard to say who's a scavenger
%§2 - it's even more problematic in the fossil record but people have tried some indirect approaches
%§3 - good thing is that we can apply these indirect approaches to extant systems
%§4 - in this review we discuss some stuff.
%TG: or something along these lines, obviously flexible!
Historically, scavengers have not been viewed as the most charismatic animals. This may go some way to explaining the gap in our knowledge of the prevalence of this behaviour. Prof Sanborn Tenney writing in 1877 for The American Naturalist had this to say about one well known group, “Prominent among the mammalian scavengers are the hyenas, the ugliest in their general appearance of all the flesh eaters.” He contrasts these with “nobler kinds” of carnivores such as lions and tigers. Even aside from our own subjective biases, scavenging is a difficult behaviour to detect after the fact. Without catching a carnivore in the act of killing we are left to infer how the prey was killed. Some simple heuristics can inform us, for instance, in cases where the prey item was simply too large to have been killed by the ostensible predator. But clearly, a scavenger doesn’t only feed on animals too big for it to have hunted. 
This is significant, because as we are now beginning to realise, the extent of this behaviour is enormous among the carnivores such that, “in some ecosystems, vertebrates have been documented to assimilate as much as 90\% of the available carrion" \citep{benbow2015introduction}. Even Tenney’s noble big cats are now known to take in a significant portion of carrion in their diet where some lion populations get over 50\% of their meat from carcasses.
The obvious lack of direct behavioural data compounds the difficulty of discerning scavenging among extinct forms. Indeed, a single species of dinosaur notwithstanding, a synthesis describing the natural history of scavengers is absent from the literature.

@@

"\cite{sazima1990necrofagia} predicted that  several components  of  snake  be-havior contribute to scavenging propensity. They  postulated  that  snakes  that  rely  on chemosensory information to acquire prey might forage  for  carrion  more  frequently than  those  whose  modes  of prey acquisition are driven by visual cues. Additionally, \cite{sazima1990necrofagia} suggested that habitat and diet preferences might be indicators of scavenging   propensity   be-cause  they  influence  the  likelihood of a particular species encountering carrion naturally. Based on these criteria, they pre-dicted that aquatic or semi-aquatic pisciv-orous snakes  would  scavenge  more  fre-quently than other species. Moreover, \cite{sazima1990necrofagia}  suggested that water currents that induce  aggrega-tions of carrion heighten the probability of carrion detection by these snakes (see also \cite{savitzky1992laboratory}).  Also,  chemical  gradients may  be  more  uniform  and  give  more  de-pendable  directional information in water \citep{sazima1990necrofagia}." \citep{devault2002scavenging}
